Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-15 chi2012.tex
tense wrestling

\begin{abstract}
Exploratory sequential mixed method study
\end{abstract}

@@

In recent years, an unprecedented quantity and variety of information has been made available as structured data on the Web, through APIs, datasets, and data feeds.  This information includes: access to data previously hidden behind services and applications, such as retailer product catalogues; information not previously directly released to the public, such as open government data or records of personal financial transactions; and new kinds of data generated by emerging kinds of data sources, such as wearable and smartphone-based biosensors.  While a primary goal of opening up such direct access to information is that end-user citizens will make more informed decisions pertaining to their personal information, for example health, wealth, and well-being \cite{}.  This data is predominately used by  specialised app developers, journalists and other ``data specialists'' but remains inaccessible to citizens because of the available tools.  For example, the most commonly used structured personal information management (PIM) tools either manage a small, fixed set of data types (such as digital calendaring tools and  to-do list managers) or provide little or no support for structured data at all, such as text editors and sketching/drawing tools \cite{}.

We hypothesise that end-users would benefit from this rich data with tools allowing them to effectively browse, use and consume heterogeneous structured data from diverse sources.  In this paper, we aim to investigate how extending PIM tools to effectively use emerging ecosystems of personal data would impact information practice.  We use a three stage sequential exploratory mixed method approach: First, we performed a qualitative analysis, using a small semi-structured interview study to examine the types of tasks people perform requiring more than one source of information, and the processes that they would use to perform such a task.  Our results suggest that people prefer to rely upon multiple, diverse sources to singular integrated ones for a number of reasons, including coverage, reliability, and seeking out more suitable alternatives.

Second, we conducted a quantitative analysis of various popular personal data sources available today to identify potential barriers to effective unification of data from each.  We then draw upon definitions and work from the database integration systems literature to characterise types of heterogeneity exhibited across data sources in three popular domains: social networking, shopping, and dining, finding that terminological heterogeneity dominates the simpler data feeds (including social networking and restaurant recommendations), while structural issues pervade the more complex schemas of online retailers' product catalogues.

>>>>

\begin{abstract}
Exploratory sequential mixed-method study
\end{abstract}

@@

In recent years, an unprecedented quantity and variety of information has been made available as structured data on the Web, through APIs, datasets, and data feeds.  This information includes: access to data previously hidden behind services and applications, such as retailer product catalogues; information not previously directly released to the public, such as open government data or records of personal financial transactions; and new kinds of data generated by emerging kinds of data sources, such as wearable and smartphone-based biosensors.  A primary goal of opening up such direct access to information is that end-user citizens will make more informed decisions pertaining to their personal information, for example health, wealth, and well-being \cite{}.  This data is predominately used by  specialised app developers, journalists and other ``data specialists'' but remains inaccessible to citizens because of the available tools.  For example, the most commonly used structured personal information management (PIM) tools either manage a small, fixed set of data types (such as digital calendaring tools and  to-do list managers) or provide little or no support for structured data at all, such as text editors and sketching/drawing tools \cite{}.

We hypothesise that end-users would benefit from this rich data with tools allowing them to effectively browse, use and consume heterogeneous structured data from diverse sources.  In this paper, we present our investigation of how extending PIM tools to effectively use emerging ecosystems of personal data impact information practice.  We used a three stage sequential exploratory mixed-method approach: first, we performed a qualitative analysis of a semi-structured interview pre-study to understand the types of tasks people performed using a plurality of  information sources, and the processes that they relied upon to perform such tasks.  Our results suggested that people preferred to rely upon multiple, diverse sources to singular, integrated ones for a number of reasons, including coverage, reliability, and seeking out more suitable alternatives.

Second, we conducted a quantitative, structural analysis of various popular personal data sources available today to identify potential barriers to effective unification of data from each.  Drawing upon definitions from the database integration and automatic schema matching literature, we characterised the types of heterogeneity exhibited across data sources in three popular domains: social networking, shopping, and dining, finding that terminological heterogeneity dominates the simpler data feeds (including social networking and restaurant recommendations), while structural issues pervade the more complex schemas of online retailers' product catalogues.
